%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% Research Summary
%%%
%%% Author - Steve Hurder
%%%
%%% Date Started: October 12, 2009
%%% Date Completed: November 15 , 2009
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{amsart}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{hyperref}



\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\newcommand{\student}[1]{\vspace{.5cm}\fbox{\parbox{0.95\linewidth}{{\small #1}}}\vspace{.5cm}}
\newcommand{\abr}[1]{\textsc{#1}}

\begin{document}

 \title{Statement on Diversity}

 \author{Jordan Boyd-Graber}
\address{University of Maryland}
\email{jbg@boydgraber.org}

\date{July 2022}


\keywords{}

\maketitle

\section{My Background}

My background is fairly privelidged: in the lingo, I'm a white, cishet, relatively able-bodied male who was able to attend an ivy-league graduate school.
%
I was born in the \abr{us}, speak English as my first language, and other than being raised in a minority religion, exemplify the demographics that are have been overrepresented in American academia.

Where my background can build connections and empathy with disadvantaged groups is that I grew up on a relatively poor background: my mom was the first in her family to graduate college, and she only did that after I was born.
%
Thus, I observed my mom's struggle as a single mother to work cleaning models and navigate the welfare system through her undergrad degree and her graduate degree.

The relatively stable life that we had afterward helped illuminate the value of education.
%
The forgiveness and grace that her teachers and mentors showed her (i.e., when childcare fell through and she had to bring me to class) serve as models for how I try to be flexible and understanding to my own students.
%
And this is also why I prefer to work and teach in public institutions; the investments that the \abr{us} federal government and the state of Illinois made in education allowed my mother and myself to have a better life; private institutions that only teach a handful of students do not effectively serve all of society.

\section{Mentoring Diverse Students}

And I try to take that broad approach toward recruiting my research group.
%
Not just for altruistic, egalitarian reasons\dots it helps expose me to new research topics.
%
Working with a blind student helped motivate our research on new ways of explaining the output of machine learning models without relying on graphical visualizations.
%
Working with a hispanic student helped open my eyes to the skewed demographic assumptions of question answering dataset that mostly talks about white, American men.
%
Mentoring an African-American student who went on to a faculty position has been particularly eye opening: both from the advice I gave him, his struggles with students, and his insane workload from being the departments only faculty of color.

This has helped me to realize the importance of advocating for diverse candiates at the University of Maryland (although not as successfully as I'd like) and to help build our programs to be more diverse.
%
During grad school, my first advisor was Maria Klawe (until she left to become president of Harvey Mudd), who helped open my eyes to the slow attrition of underrepresented groups in the undergraduate pipeline.
%
In designing the new undergraduate information science major, we specifically tried to avoid these ``weed out'' traps; compared to computer science, it has substantially better diversity (31\% from underrepresented groups vs. 13\% for computer science) while also being close to gender parity.

\section{Knowledge for All}

Beyond the walls of my university, I also feel I have an obligation to broadly disseminate knowledge: I open source the code to all of my research projects and ensure that this is written into the contract language; I post all of my lectures online for anyone to view (with accessible subtitles); and I regularly offer remote research opportunities to students.
%
I do this because I know that not everyone has the resources to access expensive education but that nonetheless almost anyone can benefit from knowledge.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliographystyle{../style/acl}
%\bibliography{../bib/journal-full,../bib/jbg}

\end{document}
