%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%% Research Summary
%%%
%%% Author - Steve Hurder
%%%
%%% Date Started: October 12, 2009
%%% Date Completed: November 15 , 2009
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{amsart}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}


\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}

\newcommand{\student}[1]{\vspace{.5cm}\fbox{\parbox{0.95\linewidth}{{\small #1}}}\vspace{.5cm}}
\newcommand{\abr}[1]{\textsc{#1}}

\begin{document}

 \title{Statement on Academic Self-Administration and Service}

 \author{Jordan Boyd-Graber}
\address{University of Maryland}
\email{jbg@boydgraber.org}

\date{July 2022}


\keywords{}

\maketitle

\section{Director of the Computational Linguistics Lab}

At the University of Maryland, I served at the director of the
computational linguistics lab 2018--2022 (with a pause in the middle
while I was on sabbatical).
%
This requires advocating for resources for the lab: money to host
visitors, space to seat students, and time from technical staff to
support our computational resources.
%
More importantly, it is also the director's responsibility to bring
the ten tenure-track faculty for building consensus and shared
decision making on matters ranging from printer placement to student
discipline.

During this time, we had to substantially rebuild our computational
infrastructure.
%
When I took over as director, the lab was primarily using \abr{cpu}
nodes with data stored on \abr{zfs} on its own monolithic cluster.
%
As I'm wrapping up my term, we have moved to a cluster that's shared
with other research groups with high-memory \abr{gpu}s backed by a
modern distributed filesystem.
%
Making this transition required lobbying for funding, working with the
technical staff to implement the changes, coordinating equipment
purchases on individual grant purchases, and then instructing students
on how to use the equipment as we navigate these transitions.

Apart from these computational changes, we also navigated the
transition from fully online to hybrid interactions, which required
exhorting students to follow the university's guidance on social
distancing and mask wearing and supporting students and faculty
working from home through alternate means of participating in lab
life.

\section{Professional Service}

I organized the 2015 \abr{acl} student research workshop with
\abr{nsf} support, which helps introduce students to the research
community.

In addition to reviewing articles for journals and conferences, I've
served as an area chair for a variety of topics (mostline machine
learning, topic clustering, and question answering) at top-tier venues
like \abr{emnlp}, \abr{acl}, \abr{neurips}, \abr{icml}, and
\abr{naacl}.  

In 2022, after complaining about how hybrid conferences created a
``separate but equal'' status for virtual attendees, I was invited to
be \abr{emnlp}'s first virtual poster chair.
%
Our goal is to use technology and prioritizing cross-modal interaction
to make sure that those unable to be in Abu Dhabi---either because of
visa status, health, or family obligations---are still able to
interact and be visible.


% TODO: Corona, virtual poster session chair

% TODO: CLIP Director

\section{Creating a New Undergraduate Curriculum}

From 2011--2013, I chaired \abr{umd}'s Information Science undergraduate
education committee. During this time, we developed a new undergraduate degree
program to complement the university's existing strengths (and exploding
enrollments) in computer science. I developed the initial proposal,
articulation agreements with local community colleges, planned course
offerings, and shepherded the proposal through college, provost, and
state (Bundesland) approval.
%
Susan Winter and Vedat Diker (and many others) took over the actual
implementation of the program, which became the university's fastest growing
major (958 majors in less than five years of existence).

This was not easy.  I had to convince elements within the college that an undergraduate
program was indeed a good idea and would not distract or detract from the
College's existing (graduate-only) programs that were already stable,
successful (both academically and financially), and well understood.
%
I crafted a data-driven message (using a topic model analysis) that convinced
faculty holdouts and the administration that we should continue a new
undergraduate program that would be well-received by potential students.

We then created a set of concentrations, courses, and schedules to offer the
courses for initial cohorts.  We drafted course descriptions, learning outcomes,
and worked with feeder programs to work out prerequisites.  

\section{Building the Faculty}

Apart from the undergraduate program, the largest investment of my
time in university service is in recruiting new faculty.
%
At Colorado, I served on the search committee that 
hired Jed Brown, Raf Frongillo, and Matt Hammer and lead the
recruitment of Raf Frongillo.
%
The following year, Martha Palmer and I successfully recruited Chenhao
Tan.

At Maryland, I served two years on a search committee for a joint hire
between the iSchool and Journalism (the first year failed) that hired
Naeemul Hassan.
%
Within computer science, I was a part of the search committee that
hired Rachel Rudinger, and I led her recruitment.

Because of my joint appointment across four units at Maryland, I have served as mentor
for a number of faculty: Yla Tausczik, Rachel Rudinger, Babak Fotouhi,
and Naeemul Hassan.

% Chenhao Tan

\section{Outreach to Undergraduates and High Schools}

% Mentoring the academic quiz team

My research is---in part---about human vs. computer question answering
competitions, so it's only natural that I also support our
undergraduate students who compete against other schools in academic
competitions.

The University of Colorado had previously not competed in these
events.
%
I organized three local high school tournaments to raise funds for so that
students could have the funds to travel to national competitions, which
they did for the first time in 2016 after winning their region.
%
I've done this in collaboration with groups of passionate
undergraduates who develop both competition-specific skills and more
general leadership skills.

At Maryland, I advise an existing academic team that
consistently is in the top ten nationally.
%
I help advise the club leadership, provide institutional memory, and
connect the club with external organizations (e.g., setting up
cross-university scrimmages between \abr{umd} and Howard).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\bibliographystyle{../style/acl}
%\bibliography{../bib/journal-full,../bib/jbg}

\end{document}
