%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.0 (10/2/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{resume_src/structure} % Include structure.tex which contains packages and document layout definitions

\newcommand*{\addExperience}[4]{
        \vspace{2mm}
	{\bf #1} \hfill #2      \\
	{\sl #3} \hfill \emph{ #4}\\
}

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{Jordan Boyd-Graber}{}  % Your name and date of birth or subtitle

\noindent\href{mailto:jbg@umiacs.umd.edu}{jbg@umiacs.umd.edu}\bull % Your email address
\textsmaller{+}1 (920) 524-9464\bull \href{http://umiacs.umd.edu/~jbg}{\url{http://umiacs.umd.edu/~jbg}}\\ % Your URL
Iribe 4146 \bull Computer Science \bull iSchool \bull College Park, MD

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Summary} % Root section title

\vspace{-1.3em} % Reduce whitespace after the Summary heading and the two-column content

\begin{multicols}{2}  % Start a two-column layout

Jordan Boyd-Graber's research focus is in applying machine learning
to problems that help computers better
work with or understand humans.  His research
applies statistical models to natural language problems in ways that
interact with humans, learn from humans, or help researchers
understand humans.

Jordan is an expert in the application of topic models, automatic
tools that discover structure and meaning in large, multilingual
datasets. His work has been supported by NSF, DARPA, IARPA, and ARL.

Three of his students have gone on to tenure track positions at NYU, U
Mass Amherst, and Ursinus.

His awards include a 2017 NSF CAREER, the Karen Sp\"ark Jones prize;
``best of'' awards at NIPS, CoNLL, EMNLP, and NAACL; and a Computing
Innovation Fellowship (declined).  His Erd\"os number is 2 (via Maria Klawe), and his
Bacon number is 3 (by embarassing himself on \textit{Jeopardy!}).

\end{multicols}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Positions Held} % Top level section


%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{\href{http://umiacs.umd.edu}{University of Maryland}}
{\textsc{College Park, MD}} {

\headedsubsection % Job title entry for the current employer
{Associate Professor in Computer Science, UMIACS, and iSchool}
{2017--Present}
{}


\headedsubsection % Job title entry for the current employer
{Assistant Professor in the Institute for Advanced Computer Studies}
{2011--2014}
{}

\headedsubsection % Job title entry for the current employer
{Assistant Professor of Information Studies (iSchool)}
{2010--2014}
{}

}

\headedsection
{\href{http://cs.colorado.edu/}{University of Colorado Boulder}}
{\textsc{Boulder, CO}} {

\headedsubsection % Job title entry for the current employer
{Assistant Professor of Computer Science}
{2014--2017}
{}

\headedsubsection % Job title entry for the current employer
{Associate Professor of Computer Science}
{2017}
{}
}


\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Princeton University}
{\textsc{Princeton, NJ}} {

\headedsubsection % Job title entry for the current employer
{Ph.D. in Computer Science}
{2004 -- 2010}
{\bodytext{Advisor: David Blei; Thesis: Linguistic Extensions of Topic Models}}
}

%------------------------------------------------

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{California Institute of Technology}
{\textsc{Pasadena, CA}} {

\headedsubsection % Job title entry for the current employer
{B.S. in Computer Science and History (dual degree)}
{2000 -- 2004} {}
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Selected Publications} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Note:}
{Students I have advised are \underline{underlined}.}

\begin{multicols}{2}  % Start a two-column layout

\small

\begin{enumerate*}

\item Chenglei Si, Navita Goyal, Tongshuang Wu, Chen Zhao, Shi Feng, Hal Daum\'{e} {III}, and {\bf Jordan Boyd-Graber}.  {\bf \href{http://cs.umd.edu/~jbg//docs/2024_naacl_convincingly.pdf}{Large Language Models Help Humans Verify Truthfulness---Except When They Are Convincingly Wrong}}.  \emph{North American Association for Computational Linguistics}, 2024.
  
\item Sander V Schulhoff, Jeremy Pinto, Anaum Khan, Louis-François Bouchard, \underline{\href{https://noviscl.github.io/}{Chenglei Si}}, Jordan Lee Boyd-Graber, Svetlina Anati, Valen Tagliabue, Anson Liu Kost, and Christopher R Carnahan.  {\bf \href{http://umiacs.umd.edu/~jbg//docs/2023_emnlp_hackaprompt.pdf}{Ignore This Title and HackAPrompt: Exposing Systemic Vulnerabilities of LLMs Through a Global Prompt Hacking Competition}}.  \emph{Empirical Methods in Natural Language Processing}, 2023.

\item Shi Feng and {\bf Jordan Boyd-Graber}.  {\bf \href{http://cs.umd.edu/~jbg//docs/2022_emnlp_augment.pdf}{Learning to Explain Selectively: A Case Study on Question Answering}}.  \emph{Empirical Methods in Natural Language Processing}, 2022.
  
	 \item Alexander Hoyle, Pranav Goel, \underline{\href{http://denispeskov.github.io/}{Denis Peskov}}, Andrew Hian-Cheong, {\bf Jordan Boyd-Graber}, and Philip Resnik.  {\bf \href{http://umiacs.umd.edu/~jbg//docs/2021_neurips_incoherence.pdf}{Is Automated Topic Model Evaluation Broken?: The Incoherence of Coherence}}.  \emph{Neural Information Processing Systems}, 2021.

  
\item \underline{\href{http://www.ericswallace.com/}{Eric Wallace}}, \underline{\href{https://www.pedro.ai}{Pedro Rodriguez}}, \underline{\href{http://users.umiacs.umd.edu/~shifeng/}{Shi Feng}}, Ikuya Yamada, and {\bf Jordan Boyd-Graber}.  {\bf Trick Me If You Can: Human-in-the-loop Generation of Adversarial Question Answering Examples}.  \emph{Transactions of the Association of Computational Linguistics}, 2019.

\item {\bf Jordan Boyd-Graber}, Yuening Hu, and David Mimno.  {\bf \href{http://www.nowpublishers.com/article/Details/INR-030}{Applications of Topic Models}}.  2017.

\item \underline{Mohit Iyyer}, Anupam Guha, Snigdha Chaturvedi, {\bf Jordan Boyd-Graber}, and Hal {Daum\'{e} III}.  {\bf \href{http://cs.colorado.edu/~jbg//docs/2016_naacl_relationships.pdf}{Feuding Families and Former Friends: Unsupervised Learning for Dynamic Fictional Relationships}}.  \emph{North American Association for Computational Linguistics}, 2016.

	 \item \underline{\href{http://www.umiacs.umd.edu/~hhe/}{He He}}, {\bf Jordan Boyd-Graber}, Kevin Kwok, and Hal {Daum\'{e} III}.  {\bf \href{http://umiacs.umd.edu/~jbg//docs/2016_icml_opponent.pdf}{Opponent Modeling in Deep Reinforcement Learning}}.  \emph{International Conference on Machine Learning}, 2016.

\item Alvin {Grissom II}, {\bf Jordan Boyd-Graber}, He He, John Morgan, and Hal {Daum\'{e} III}.  {\bf Don't Until the Final Verb Wait: Reinforcement Learning for Simultaneous Machine Translation}.  \emph{Empirical Methods in Natural Language Processing}, 2014.


\item Jonathan Chang, {\bf Jordan Boyd-Graber}, Chong Wang, Sean Gerrish,
and David M. Blei.  {\bf Reading Tea Leaves: How Humans Interpret
  Topic Models}.  \emph{Neural Information Processing Systems}, 2009.



\end{enumerate*}

\end{multicols}

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Natural languages:}
{English \textit{(native)}, German \textit{(working)}, and Mandarin Chinese \textit{(beginner)}.}

%------------------------------------------------


\end{document}
